---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# dabestr 

<!-- badges: start -->
[![Travis CI build status](https://img.shields.io/travis/com/ACCLAB/dabestr/master.svg)](https://travis-ci.com/ACCLAB/dabestr/) [![minimal R version](https://img.shields.io/badge/R%3E%3D-2.10-6666ff.svg)](https://cran.r-project.org/) [![CRAN Download Count](https://cranlogs.r-pkg.org/badges/grand-total/dabestr?color=brightgreen)](https://cran.r-project.org/package=dabestr) [![Free-to-view citation](https://zenodo.org/badge/DOI/10.1038/s41592-019-0470-3.svg)](https://rdcu.be/bHhJ4) [![License](https://img.shields.io/badge/License-Apache_2.0-orange.svg)](https://spdx.org/licenses/BSD-3-Clause-Clear.html)
[![R-CMD-check](https://github.com/sunroofgod/dabestr-prototype/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/sunroofgod/dabestr-prototype/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

<!-- ## Overview -->
dabestr is a package for **D**ata **A**nalysis using **B**ootstrap-Coupled **EST**imation.

[Estimation statistics](https://en.wikipedia.org/wiki/Estimation_statistics "Estimation Stats on Wikipedia") is a [simple framework](https://thenewstatistics.com/itns/ "Introduction to the New Statistics") that avoids the [pitfalls](https://www.nature.com/articles/nmeth.3288 "The fickle P value generates irreproducible results, Halsey et al 2015") of significance testing. It uses familiar statistical concepts: means, mean differences, and error bars. More importantly, it focuses on the effect size of one's experiment/intervention, as opposed to a false dichotomy engendered by *P* values.

An estimation plot has two key features.

1.  It **presents all datapoints** as a swarmplot, which orders each point to display the underlying distribution.

2.  It presents the **effect size** as a **bootstrap 95% confidence interval** on a **separate but aligned axes**.

## Installation

```{bash, eval = FALSE}
git clone https://github.com/ACCLAB/dabestr
```

## Usage

```{r, include = FALSE}
devtools::load_all(".")
```

```{r}
data(twogroup_data)

dabest_obj.mean_diff <- dabestr::load(data = twogroup_data, 
                                      x = Group, 
                                      y = Measurement, 
                                      idx = c("Control1", "Group1")) %>%
  dabestr::mean_diff()

dabest_plot(dabest_obj.mean_diff, TRUE)
```


## Citation 

**Moving beyond P values: Everyday data analysis with estimation plots**

*Joses Ho, Tayfun Tumkaya, Sameer Aryal, Hyungwon Choi, Adam Claridge-Chang*

Nature Methods 2019, 1548-7105. [10.1038/s41592-019-0470-3](http://dx.doi.org/10.1038/s41592-019-0470-3)

[Paywalled publisher site](https://www.nature.com/articles/s41592-019-0470-3); [Free-to-view PDF](https://rdcu.be/bHhJ4)

## Contributing

All contributions are welcome; please read the [Guidelines for contributing](https://github.com/ACCLAB/dabestr/blob/master/CONTRIBUTING.md) first.

We also have a [Code of Conduct](https://github.com/ACCLAB/dabestr/blob/master/CODE_OF_CONDUCT.md) to foster an inclusive and productive space.

## Dabestr in other languages

dabestr is also available in [Python](https://github.com/ACCLAB/DABEST-python "DABEST-Python on Github") and [Matlab](https://github.com/ACCLAB/DABEST-Matlab "DABEST-Matlab on Github").
