---
title: "Controlling Plot Aesthetics"
output: rmarkdown::html_vignette
description: |
  Loading in of sample datasets for dabestr.
vignette: >
  %\VignetteIndexEntry{Controlling Plot Aesthetics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

Controlling plot aesthetics is very simple in dabestr. An integral part to the 
design of dabestr is to allow its users to freely adjust the various components
of a DABEST estimation plot, allowing for the most ideal looking plot to be
produced.

## Getting started
At this point, we assume that you have already obtained the `dabest_effectsize_obj`.
To add and adjust specific plot components, simply add it as a argument into the 
`dabest_plot()` function. If you're missing a step, start from `load()`.

```{r, eval = FALSE}
dabest_plot(
  dabest_effectsize_obj,
  float_contrast = TRUE,
  swarm_label = "value",
  contast_label = "effect size",
  swarm_x_text = 11,
  swarm_y_text = 15,
  contrast_x_text = 11,
  contrast_y_text = 15,
  contrast_ylim = NULL,
  swarm_ylim = NULL,
  raw_marker_size = 1.5,
  tufte_size = 0.8,
  es_marker_size = 0.5,
  es_line_size = 0.8,
  raw_marker_spread = 2,
  show_delta2 = FALSE,
  show_mini_meta = FALSE,
  delta2_ylim = NULL,
  delta2_label = NULL,
  raw_marker_alpha = 1,
  raw_bar_width = 0.3,
  asymmetric_side = "right",
  raw_marker_side_shift = 0,
  sankey= TRUE,
  flow= TRUE,
  show_zero_dot= TRUE,
  show_baseline_ec = FALSE,
  custom_palette = "d3"
)
```


## Adjusting Text
All text elements in the estimation plot can be adjusted. This includes the value,
the size and even removal of the text elements completely.

### Size
This is the list of parameters for adjusting the size of the text elements.

- `swarm_x_text`: Default 11. Numeric value determining the font size of the x-axis of the swarm plot.
- `swarm_y_text`: Default 15. Numeric value determining the font size of the y-axis of the swarm plot.
- `contrast_x_text`: Default 11. Numeric value determining the font size of the x-axis of the contrast plot.
- `contrast_y_text`: Default 15. Numeric value determining the font size of the y-axis of the contrast plot.

```{r, include = FALSE}
devtools::load_all(".")
data(twogroup_data)
dabest_twogroup_obj.mean_diff <- load(twogroup_data, x = Group, y = Measurement, idx = c("Control1", "Group1")) %>% 
  mean_diff()
```

```{r}
dabest_plot(
  dabest_twogroup_obj.mean_diff, 
  float_contrast = TRUE, 
  swarm_x_text = 30, 
  swarm_y_text = 1, 
  contrast_x_text = 30, 
  contrast_y_text = 5
)
```

### Labels
This is the list of parameters for adjusting the label of the text elements.

- `swarm_label`: Default "value" or "proportion of success" for proportion plots. Label for the y-axis of the swarm plot.
- `contrast_label`: Default "effect size", based on the effect sizes as given in [effect_size()]. Label for the y-axis of the contrast plot.
- `delta2_label`: Default NULL. Label for the y-label for the delta-delta plot. 

```{r}
dabest_plot(
  dabest_twogroup_obj.mean_diff, 
  float_contrast = TRUE, 
  swarm_label = "I love estimation statistics.",
  contrast_label = "I love it more than you do!"
)
```